{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
use package mathpartir instead of bussproof, because of bussproofs limitation to three premisses
converted bussproofs prooftrees to mathpartirs inferrules

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{nameref}
\usepackage{url}

@@

\todo{Place proofstrees into one line with minipages}
\begin{figure}
\begin{prooftree}
\AxiomC{P[i] $\in$ SeqIns}
\AxiomC{$se, i \vdash_{seq} s \Rightarrow t$}
\BinaryInfC{$se, i \vdash s \Rightarrow t$}
\end{prooftree}

\begin{prooftree}
\AxiomC{P[i] = \texttt{start} pc}
\AxiomC{$se(i) \leq se(pc)$}
\BinaryInfC{$se, i \vdash s \Rightarrow s$}
\end{prooftree}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

\todo{beautify me}
\begin{figure}
\begin{prooftree}
\AxiomC{$P[i] = store\ x$}
\AxiomC{$se(i) \sqcup k \leq \Gamma(x)$}
\BinaryInfC{$se, i \vdash_{seq} k :: st \Rightarrow st$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$P[i] = ifeq\ j$}
\AxiomC{$\forall j' \in reg(i), k \leq se(j')$}
\BinaryInfC{$se, i \vdash_{seq} k :: st \Rightarrow lift_k(st)$}
\end{prooftree}
\caption{Excerpt of typing rules for the assembly language}
\label{fig:transfer-rules}
\end{figure}

@@

\todo{use an other package to display these rules}
\begin{figure}
\begin{prooftree}
\AxiomC{$\vdash e : L$}
\AxiomC{$\vdash_\alpha c : E$}
\AxiomC{$\vdash_\alpha c' : E$}
\LeftLabel{L-COND:\quad}
\TrinaryInfC{$\vdash_\alpha [if \ e \ then \ c \ else \ c']^n_\alpha : E$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$\vdash e : H$}
\AxiomC{$\vdash_\bullet c : E$}
\AxiomC{$\vdash_\bullet c' : E$}
\LeftLabel{H-COND:\quad}
\TrinaryInfC{$\vdash_\bullet [if \ e \ then \ c \ else \ c']^n_\bullet : E$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$\vdash e : H$ \quad $\vdash_\bullet c : E$}
\AxiomC{$\vdash_\bullet c' : E$}
\AxiomC{$E = lift_H(E, sregion(n))$}
\LeftLabel{TOP-H-COND:\quad}
\TrinaryInfC{$\vdash_\circ [if \ e \ then \ c \ else \ c']^n_\bullet : E$}
\end{prooftree}

\caption{Typing rules for \texttt{if} on source level.}
\label{fig:typing-rules-if}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{mathpartir}
\usepackage{nameref}
\usepackage{url}

@@

\todo{Place proofstrees into one line with minipages and beautify me}
\begin{figure}
\begin{align*}
\inferrule{P[i] \in SeqIns \\ se, i \vdash_{seq} s \Rightarrow t}
{se, i \vdash s \Rightarrow t}
\end{align*}

\begin{align*}
\inferrule{P[i] = \mathtt{start} pc \\ se(i) \leq se(pc)}
{se, i \vdash s \Rightarrow s}
\end{align*}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

\todo{beautify me}
\begin{figure}
\begin{align*}
\inferrule{P[i] = store\ x \\ se(i) \sqcup k \leq \Gamma(x)}
{se, i \vdash_{seq} k :: st \Rightarrow st}
\end{align*}

\begin{align*}
\inferrule{P[i] = ifeq\ j \\ \forall j' \in reg(i), k \leq se(j')}
{se, i \vdash_{seq} k :: st \Rightarrow lift_k(st)}
\end{align*}
\caption{Excerpt of typing rules for the assembly language}
\label{fig:transfer-rules}
\end{figure}

@@

\todo{use an other package to display these rules}
\begin{figure}
\begin{align*}
\inferrule[L-COND]{\vdash e : L \\ \vdash_\alpha c : E \\ \vdash_\alpha c' : E}
{\vdash_\alpha [if \ e \ then \ c \ else \ c']^n_\alpha : E}
\end{align*}

\begin{align*}
\inferrule[H-COND]{\vdash e : H \\ \vdash_\bullet c : E \\ \vdash_\bullet c' : E}
{\vdash_\bullet [if \ e \ then \ c \ else \ c']^n_\bullet : E}
\end{align*}

\begin{align*}
\inferrule[TOP-H-COND]{\vdash e : H \\ \vdash_\bullet c : E \\
\vdash_\bullet c' : E \\ E = lift_H(E, sregion(n))}
{\vdash_\circ [if \ e \ then \ c \ else \ c']^n_\bullet : E}
\end{align*}
\caption{Typing rules for \texttt{if} on source level.}
\label{fig:typing-rules-if}
\end{figure}
